\plaintitle

### 2017-01-12 chi/piecework/piecework_lit.tex
fixing final paper name and other stuff
actual forreal final version

\documentclass[trackingWork]{subfiles}
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
  \externaldocument{complexity}
  \externaldocument{relationships}
  \externaldocument{decomposition}
}
\begin{document}

@@

\topic{Piecework's history traces back further than most would likely expect.}
\citeauthor{grier2013computers} describes the process astronomers adopted of hiring teenage men
to calculate equations in order
to better--predict the trajectories of various celestial bodies in the night sky~\cite{grier2013computers}.
In the first half of the \nth{19} century, George Airy was perhaps the first to rigorously put piecework--style decomposition to work;
by breaking complex calculations into constituent parts, and
training young men to solve simple algebraic problems,
Airy could distribute work to many more people than could otherwise complete the full calculations.

\topic{Piecework began in the intellectual domain of astronomical calculations and projections,
but it found its foothold in manual labor.}
Piecework took hold in farm work~\cite{hughRaynbirdTaskWork}, % hold foothold
in textiles~\cite{restructuringPieceworkBaker,riisOtherSideLives},
on railroads~\cite{Brown01041990}, and 
elsewhere in manufacturing~\cite{10.2307/3827491} by the mid--\nth{19} century.
\topic{By \citeyear{hughRaynbirdTaskWork} we find
a concise definition of piecework
in \citeauthor{hughRaynbirdTaskWork}'s essay on piecework,
particularly driven toward encapsulating the manual labor of farmwork.}
He does this by contrasting two paradigms:
``the chief difference lies between the day--labourer,
who receives a certain some of money~\dots~for his day's work,
and the task--labourer, whose earnings depend on the quantity of work done''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} offers a number of illustrative examples:
``payment is made for each hectare which is pronounced to be well ploughed~\dots~for each living foal got from a mare;~\dots~for each living calf got''~\cite{10.2307/2338394}.
This framing gives us an intuitive sense of piecework;
``payment for results,'' as he calls it,
is not only common in practice, but
well--studied in labor economics~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

\topic{It's worth acknowledging that
``this distinction [between piece--rates and time--rates] was not completely clear--cut''~\cite{hart2013rise}.}
Employers adopted piece--rates in some aspects and
time--rates in others.
The Rowan premium system, for example,
essentially paid workers
a base rate for time plus
additional pay depending on output~\cite{rowan1901premium}.
As \citeauthor{rowan1901premium}'s premium system guaranteed an hourly rate
regardless of the worker's productive output
\textit{as well as} additional compensation tied to performance,
workers were
in some senses ``task--labourers'', but
in other senses ``day--labourers''.
This was just one of several alternatives to strict time-- and piece--rate remuneration paradigms.

In the late years of the \nth{19} century, \citeauthor{taylor1914principles}
--- a mechanical engineer with an interest in work efficiency ---
began studying and formalizing the decomposition, tracking, and management of tasks~\cite{taylor1896piece}.
In \citeyear{taylor1914principles} he published \citetitle{taylor1914principles},
concretizing an idea that had nebulously been forming,
and which he had been working out himself, for years~\cite{taylor1914principles}.
Scientific Management (and Fordism) thrust piecework into higher gear, especially as
mass manufacturing and
a depleted wartime workforce forced industry to find new ways to eke out more production capacity.

\ali{Somewhere here(?) I want to talk about Gibreth's works~\cite{gilbreth1911motion,gilbreth1911motion}. Should I save it to be the saving grace in the discussion?}

\topic{It may be worth thinking about piecework through the lens of its \textit{emergent} properties to help understand it.}
\citeauthor{hughRaynbirdTaskWork} argues for the merits of piecework,
pointing out that
``piece work holds out to the labourer an increase of wages as a reward for his skill and exertion~\dots~he knows that all depends on his own diligence and perseverance~\dots~[and] so long as he performs his work to the satisfaction of his master, he is not under that control to which the day--labourer is always subject''.
The argument that ``task--labourers'' enjoy freedom from control crops up in \citeauthor{hughRaynbirdTaskWork}'s and later \citeauthor{rowan1901premium}'s works~\cite{hughRaynbirdTaskWork,rowan1901premium}.

\topic{We see this sense of independence in myriad times, locales, and industries.}
\citeauthor{10.2307/3827491} offers a look into the lives and culture of ``match--girls'', teenage women who assembled matchsticks in the late \nth{19} century in London. % added that these women were in London since Chinmay critiqued that we're glossing over the labor advocacy movement that grew in Europe, which revealed that we completely left out the fact that this all happened in England.
\ali{Chinmay: but still not convinced; this is a post hoc ergo propter hoc argument}
Of interest was their reputation ``\dots~for generosity, independence, and protectiveness,
but also for brashness, irregularity, low morality, and little education''~\cite{10.2307/3827491}.
\citeauthor{10.2307/27508091} document piecework from 1850 through 1930 in Australia,
finding similar notions of independence and autonomy among piecework newspaper compositors:
``If a piece--work compositor~\dots~decided that he did not want to work on a particular day or night, the management recognised his right to put a `substitute' or `grass' compositor in his place''~\cite{10.2307/27508091}.
This sense of independence and autonomy appears to be a common thread of piecework.

@@

\topic{Piecework's popularity in the United States and Europe fell almost as quickly as it had climbed.}
Between 1938 and 1942, the proportion of metal workers under piecework systems had climbed steeply from 11\% to 60\%~\cite{hart2005piecework}.
By 1961, \citeauthor{carlson1982time} finds, the proportion dropped to 8\%~\cite{carlson1982time}.
He notes that, from 1973 to 1980, the holdouts of piecework
--- where more than 50\% worked under incentive wage plans ---
were principally in clothes--making (e.g. hosiery, footwear, and garments).
\citeauthor{hart2013rise} offer a number of explanations for the sudden demise of piecework.
% \ali{Should I add ``(especially in the United States but more broadly in the developed world)'' or something? Since a lot of developing nations still have sweatshops and piecework to some extent or another?}
The salient suggestions include:
\begin{inlinelist}
\item the emergence of more effective, more nuanced incentive models
--- rewarding teams for complex achievements, for instance;
\item the shifting of piecework industries such as manufacturing and textiles to other countries; and
\item the quality of ``multidimensional'' work, which was too difficult to evaluate~\cite{hart2013rise}.
\end{inlinelist}

@@

\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''~\cite{clark1908cotton}.
\end{comment}

@@

Workers could, in principle, assemble as much or as little clothing as they wanted;
the reality was more grim, as
\citeauthor{riisOtherSideLives} documented in \textit{How the Other Half Lives} in \citeyear{riisOtherSideLives}~\cite{riisOtherSideLives}.
He found that
workers endured bleak living conditions and
worked long hours attempting to scrape together a living.

@@

\topic{Regardless of what prompted it, the lasting impact of the match--girls strike of 1888 was profound.}
This was one of the earliest and most famous successful worker strikes,
and perhaps the beginning of ``militant trade unionism''~\cite{10.2307/3827491}.
As \citeauthor{weyer1894history} described,
``the match--girls' victory turned a new leaf in Trade Union annals'': in the 30 years after the match--girls strike,
the Trade Union Movement enrollment grew from 20\% of eligible workers to over 60\%~\cite{weyer1894history}.

Match--girls were some of the earliest to have formed a trade union,
according to \citeauthor{booth1903life}'s account in \citeyear{booth1903life}. % ~\cite{booth1903life}.
\citeauthor{10.2307/3827491} noted that match--girls
``\dots~pooled their resources to purchase their plumes and clothes~\dots~and expressed their solidarity through small [and major] strikes''~\cite{booth1903life}.
But they were also, as \citeauthor{10.2307/3827491} confesses, known for ``brashness, irregularity, low morality, and little education''~\cite{10.2307/3827491}.
These were workers who treasured their independence, but also fiercely protected one another. % , contributing to the common good.
``Brashness'' may have detracted from their public image, but almost undoubtedly contributed to their sense of solidarity,
making their propensity to act against such unfair treatment and poor conditions understandable and maybe predictable.

\subsubsection{Industrial workers}
\topic{Piecework might be most familiar in the context of industrial and factory work, which largely defined manufacturing through the \nth{20} century.}
Before the factory assembly line arose, however, railway companies adopted piecework regimes at the turn of the \nth{20} century.
What followed was a flourishing of management practices,
as railway companies worked to find effective ways
to motivate and evaluate this skilled workforce of engineers.
\citeauthor{10.2307/23702539} takes up a case study of the Santa Fe Railway,
finding that they employed ``efficiency experts'' to develop a ``standard time''
to determine pay for each task at the company informed by
``thousands of individual operations'';
\citeauthor{10.2307/23702539} goes on to list
some of the roles required to facilitate piecework
in the early \nth{20} century
--- among them, ``piecework clerks, inspectors, and `experts'~''~\cite{10.2307/23702539}.
This oversight, while controversial
(especially among workers~\cite{american1921problem}),
paved the way for piecework to grow substantially.

\topic{The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.}
\citeauthor{hart2013rise} characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of piecework.
They attribute this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.

>>>>

\documentclass[pn4226]{subfiles}
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
  \externaldocument{complexity}
  \externaldocument{relationships}
  \externaldocument{decomposition}
}
\begin{document}

@@

\topic{Piecework's history traces back further than most would likely expect.}
Grier describes the process astronomers adopted of hiring teenage men
to calculate equations in order
to better--predict the trajectories of various celestial bodies in the night sky~\cite{grier2013computers}.
In the first half of the \nth{19} century, George Airy was perhaps the first to rigorously put piecework--style decomposition to work;
by breaking complex calculations into constituent parts, and
training young men to solve simple algebraic problems,
Airy could distribute work to many more people than could otherwise complete the full calculations.

\topic{Piecework began in the intellectual domain of astronomical calculations and projections,
but it found its foothold in manual labor.}
Piecework took hold in farm work~\cite{hughRaynbirdTaskWork}, % hold foothold
in textiles~\cite{restructuringPieceworkBaker,riisOtherSideLives},
on railroads~\cite{Brown01041990}, and 
elsewhere in manufacturing~\cite{10.2307/3827491} by the mid--\nth{19} century.
\topic{By \citeyear{hughRaynbirdTaskWork} we find
a concise definition of piecework
in Raynbird's essay on piecework,
particularly driven toward encapsulating the manual labor of farm work.}
He does this by contrasting two paradigms:
``the chief difference lies between the day--labourer,
who receives a certain some of money~\dots~for his day's work,
and the task--labourer, whose earnings depend on the quantity of work done''~\cite{hughRaynbirdTaskWork}.
Chadwick offers a number of illustrative examples:
``payment is made for each hectare which is pronounced to be well ploughed~\dots~for each living foal got from a mare;~\dots~for each living calf got''~\cite{10.2307/2338394}.
This framing gives us an intuitive sense of piecework;
``payment for results,'' as he calls it,
is not only common in practice, but
well--studied in labor economics~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

\topic{It's worth acknowledging that
``this distinction [between piece--rates and time--rates] was not completely clear--cut''~\cite{hart2013rise}.}
Employers adopted piece--rates in some aspects and
time--rates in others.
The Rowan premium system, for example,
essentially paid workers
a base rate for time plus
additional pay depending on output~\cite{rowan1901premium}.
As Rowan's premium system guaranteed an hourly rate
regardless of the worker's productive output
\textit{as well as} additional compensation tied to performance,
workers were
in some senses ``task--labourers'', but
in other senses ``day--labourers''.
This was just one of several alternatives to strict time-- and piece--rate remuneration paradigms.

In the late years of the \nth{19} century, Taylor
--- a mechanical engineer with an interest in work efficiency ---
began studying and formalizing the decomposition, tracking, and management of tasks~\cite{taylor1896piece}.
In \citeyear{taylor1914principles} he published \textit{The principles of scientific management},
concretizing an idea that had nebulously been forming,
and which he had been working out himself, for years~\cite{taylor1914principles}.
Scientific Management (and Fordism) thrust piecework into higher gear, especially as
mass manufacturing and
a depleted wartime workforce forced industry to find new ways to eke out more production capacity.

\topic{It may be worth thinking about piecework through the lens of its \textit{emergent} properties to help understand it.}
Raynbird argues for the merits of piecework,
pointing out that
``piece work holds out to the labourer an increase of wages as a reward for his skill and exertion~\dots~he knows that all depends on his own diligence and perseverance~\dots~[and] so long as he performs his work to the satisfaction of his master, he is not under that control to which the day--labourer is always subject''.
The argument that ``task--labourers'' enjoy freedom from control crops up in Raynbird's and later Rowan's works~\cite{hughRaynbirdTaskWork,rowan1901premium}.

\topic{We see this sense of independence in myriad times, locales, and industries.}
Satre offers a look into the lives and culture of ``match--girls'', teenage women who assembled matchsticks in the late \nth{19} century in London. % added that these women were in London since Chinmay critiqued that we're glossing over the labor advocacy movement that grew in Europe, which revealed that we completely left out the fact that this all happened in England.
% \ali{Chinmay: but still not convinced; this is a post hoc ergo propter hoc argument}
Of interest was their reputation ``\dots~for generosity, independence, and protectiveness,
but also for brashness, irregularity, low morality, and little education''~\cite{10.2307/3827491}.
Hagan and Fisher document piecework from 1850 through 1930 in Australia,
finding similar notions of independence and autonomy among piecework newspaper compositors:
``If a piece--work compositor~\dots~decided that he did not want to work on a particular day or night, the management recognised his right to put a `substitute' or `grass' compositor in his place''~\cite{10.2307/27508091}.
This sense of independence and autonomy appears to be a common thread of piecework.

@@

\topic{Piecework's popularity in the United States and Europe fell almost as quickly as it had climbed.}
Between 1938 and 1942, the proportion of metal workers under piecework systems had climbed steeply from 11\% to 60\%~\cite{hart2005piecework}.
By 1961, Carlson finds, the proportion dropped to 8\%~\cite{carlson1982time}.
He notes that, from 1973 to 1980, the holdouts of piecework
--- where more than 50\% worked under incentive wage plans ---
were principally in clothes--making (e.g. hosiery, footwear, and garments).
Hart and Roberts offer a number of explanations for the sudden demise of piecework.
% \ali{Should I add ``(especially in the United States but more broadly in the developed world)'' or something? Since a lot of developing nations still have sweatshops and piecework to some extent or another?}
The salient suggestions include:
\begin{inlinelist}
\item the emergence of more effective, more nuanced incentive models
--- rewarding teams for complex achievements, for instance;
\item the shifting of piecework industries such as manufacturing and textiles to other countries; and
\item the quality of ``multidimensional'' work, which was too difficult to evaluate~\cite{hart2013rise}.
\end{inlinelist}

@@

\ali{\citeauthor{clark1908cotton}} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''~\cite{clark1908cotton}.
\end{comment}

@@

Workers could, in principle, assemble as much or as little clothing as they wanted;
the reality was more grim, as
Riis documented in \textit{How the Other Half Lives} in \citeyear{riisOtherSideLives}~\cite{riisOtherSideLives}.
He found that
workers endured bleak living conditions and
worked long hours attempting to scrape together a living.

@@

\topic{Regardless of what prompted it, the lasting impact of the match--girls strike of 1888 was profound.}
This was one of the earliest and most famous successful worker strikes,
and perhaps the beginning of ``militant trade unionism''~\cite{10.2307/3827491}.
As Webb and Webb described,
``the match--girls' victory turned a new leaf in Trade Union annals'': in the 30 years after the match--girls strike,
the Trade Union Movement enrollment grew from 20\% of eligible workers to over 60\%~\cite{weyer1894history}.

Match--girls were some of the earliest to have formed a trade union,
according to Booth's account in \citeyear{booth1903life}. % ~\cite{booth1903life}.
Satre noted that match--girls
``\dots~pooled their resources to purchase their plumes and clothes~\dots~and expressed their solidarity through small [and major] strikes''~\cite{booth1903life}.
But they were also, as Satre confesses, known for ``brashness, irregularity, low morality, and little education''~\cite{10.2307/3827491}.
These were workers who treasured their independence, but also fiercely protected one another. % , contributing to the common good.
``Brashness'' may have detracted from their public image, but almost undoubtedly contributed to their sense of solidarity,
making their propensity to act against such unfair treatment and poor conditions understandable and maybe predictable.

\subsubsection{Industrial workers}
\topic{Piecework might be most familiar in the context of industrial and factory work, which largely defined manufacturing through the \nth{20} century.}
Before the factory assembly line arose, however, railway companies adopted piecework regimes at the turn of the \nth{20} century.
What followed was a flourishing of management practices,
as railway companies worked to find effective ways
to motivate and evaluate this skilled workforce of engineers.
Graves takes up a case study of the Santa Fe Railway,
finding that they employed ``efficiency experts'' to develop a ``standard time''
to determine pay for each task at the company informed by
``thousands of individual operations'';
Graves goes on to list
some of the roles required to facilitate piecework
in the early \nth{20} century
--- among them, ``piecework clerks, inspectors, and `experts'~''~\cite{10.2307/23702539}.
This oversight, while controversial
(especially among workers~\cite{american1921problem}),
paved the way for piecework to grow substantially.

\topic{The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.}
Hart and Roberts characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of piecework.
They attribute this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.

### 2017-01-12 chi/piecework/relationships.tex
fixing final paper name and other stuff
actual forreal final version

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

@@

Workers' relationships with requesters are fraught.
The unbridled power that requesters have over workers, and
the resultant frustration that this generates,
has motivated research into
the tense relationships between workers and requesters~\cite{fixingChaos,dynamo}.
Workers are often blamed for any low--quality work, regardless of whether they are responsible~\cite{martin2014being,takingAHITMcInnis}.
Some research is extremely open about this position, blaming unpredictable work on ``malicious'' workers~\cite{MaliciousCrowdworkersGadiraju} or those with ``a lack of expertise, dedication [or] interest''~\cite{Sheng:2008:GLI:1401890.1401965}.
Workers resent this position, and for good reason.
\citeauthor{turkopticon} highlighted the information asymmetry between workers and requesters on AMT,
which led to the creation of Turkopticon, a site which allows Turkers to rate and review requesters~\cite{turkopticon}.
Dynamo then took this critique on information asymmetry and power imbalances further, designing a platform to facilitate
collective action among Turkers to changes to their circumstances~\cite{dynamo}.

@@

\topic{Early observers believed that workers were strongly motivated by the autonomy of working in the piecework model}.
\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''~\cite{clark1908cotton}.
However, the emergent trend contrasted with this early rhetoric, as
when workers began instituting ``The Fix'', deliberately slow work to game efficiency experts~\cite{roy1954efficiency}.
Piece workers, \citeauthor{roy1954efficiency} found, would form acrimonious relationships with their managers.

@@

\topic{Relative to the modern on--demand workers, there is a noticeable dearth of information on the interpersonal relationships among pieceworkers
beyond the match--girls at the end of the \nth{19} century.}
Nevertheless, we can offer some observations:
primary sources indicate that labor organizations wished for workers to identify as a collective group, 
``not only as railroad employees but also as members of the larger life of the community''~\cite{american1921problem}.
Doing this, 
\citeauthor{ostrom1990governing} and others later argued,
would facilitate collective action and perhaps collective governance~\cite{ostrom1990governing,russell1982collective,olsonlogic}.
\citeauthor{riisOtherSideLives} also contributed to this sense of shared struggle and endurance
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked~\cite{riisOtherSideLives}.

@@

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman,
% (who necessarily had an intuitive
% --- perhaps sympathetic ---
% relationship with workers),
foremen of the \nth{20} century have largely been replaced
by algorithms of the \nth{21} century~\cite{uberAlgorithm}.}
% The result of this change is that
Consequently,
the agents managing work are now
cold, logical, and unforgiving.
While a person might recognize that the ``attention check'' questions
proposed by \citeauthor{le2010ensuring} and others ensure that
malicious and inattentive workers are stopped~\cite{le2010ensuring,AAAIW113995},
some implementations of these approaches
only seem to antagonize workers~\cite{takingAHITMcInnis}.
As \citeauthor{10.2307/2555446} wrote in \citeyear{10.2307/2555446},
``when performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''~\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms.
Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.

>>>>

\documentclass[pn4226]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

@@

Workers' relationships with requesters are fraught.
The unbridled power that requesters have over workers, and
the resultant frustration that this generates,
has motivated research into
the tense relationships between workers and requesters~\cite{fixingChaos,dynamo}.
Workers are often blamed for any low--quality work, regardless of whether they are responsible~\cite{martin2014being,takingAHITMcInnis}.
Some research is extremely open about this position, blaming unpredictable work on ``malicious'' workers~\cite{MaliciousCrowdworkersGadiraju} or those with ``a lack of expertise, dedication [or] interest''~\cite{Sheng:2008:GLI:1401890.1401965}.
Workers resent this position, and for good reason.
Irani and Silberman highlighted the information asymmetry between workers and requesters on AMT,
which led to the creation of Turkopticon, a site which allows Turkers to rate and review requesters~\cite{turkopticon}.
Dynamo then took this critique on information asymmetry and power imbalances further, designing a platform to facilitate
collective action among Turkers to changes to their circumstances~\cite{dynamo}.

@@

\topic{Early observers believed that workers were strongly motivated by the autonomy of working in the piecework model}.
Clark observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''~\cite{clark1908cotton}.
However, the emergent trend contrasted with this early rhetoric, as
when workers began instituting ``The Fix'', deliberately slow work to game efficiency experts~\cite{roy1954efficiency}.
Piece workers, Roy found, would form acrimonious relationships with their managers.

@@

\topic{Relative to the modern on--demand workers, there is a noticeable dearth of information on the interpersonal relationships among pieceworkers
beyond the match--girls at the end of the \nth{19} century.}
Nevertheless, we can offer some observations:
primary sources indicate that labor organizations wished for workers to identify as a collective group, 
``not only as railroad employees but also as members of the larger life of the community''~\cite{american1921problem}.
Doing this, 
Ostrom and others later argued,
would facilitate collective action and perhaps collective governance~\cite{ostrom1990governing,russell1982collective,olsonlogic}.
Riis also contributed to this sense of shared struggle and endurance
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked~\cite{riisOtherSideLives}.

@@

\topic{The relationship between workers and employers has also shifted: while historically the management of workers had to be done through a foreman,
% (who necessarily had an intuitive
% --- perhaps sympathetic ---
% relationship with workers),
foremen of the \nth{20} century have largely been replaced
by algorithms of the \nth{21} century~\cite{uberAlgorithm}.}
% The result of this change is that
Consequently,
the agents managing work are now
cold, logical, and unforgiving.
While a person might recognize that the ``attention check'' questions
proposed by Le et al. and others ensure that
malicious and inattentive workers are stopped~\cite{le2010ensuring,AAAIW113995},
some implementations of these approaches
only seem to antagonize workers~\cite{takingAHITMcInnis}.
As Anderson and Schmittlein wrote in \citeyear{10.2307/2555446},
``when performance is difficult to evaluate,
imperfect input measures and
a manager's subjective judgment are preferable to
defective (simple, observable) output measures''~\cite{10.2307/2555446}.
This frustration has only grown as requesters have had to rely on automatic management mechanisms.
Only a few use the equivalent of human foremen~\cite{haas2015argonaut,kulkarni2012mobileworks}.
